We are excited to welcome the second batch of babies to the 2024 BabyLM Challenge. The session will be held at the Conference on Computational Natural Language Learning (CoNLL; colocated with EMNLP) on November 15, 2024 in Miami, Florida, USA. 

\vspace{1em}

This year, the program includes an oral session for the award-winning papers, and a poster session for all accepted submissions. There is also an introductory presentation from the organizers summarizing the challenge, this year's winning submissions, and trends across submissions.

\vspace{1em}

We received 31 submissions this year. A research challenge of this scale requires the participation of many parties, and we extend a big thank you to all of them. The participants' efforts are essential to advancing the state of cognitively plausible and sample-efficient language modeling---and to democratizing language modeling research.

\vspace{1em}

We also extend our sincere thanks to the CoNLL organizers for hosting the BabyLM Challenge for the second time this year. Their efforts to integrate the proceedings of this challenge have been significant, and have in turn given a home to the significant efforts of the participants.

\vspace{1em}

Finally, we thank our program committee members---largely sampled from the participants---for committing their time to help us curate an excellent program.

\vspace{1em}

---The BabyLM Organizing Committee: Michael Y. Hu, Aaron Mueller, Candace Ross,\\ Adina Williams, Tal Linzen, Chengxu Zhuang, Ryan Cotterell, Alex Warstadt, Ethan Wilcox
